Analyzing the impact of social attributes on the success of commit integration

### 2017-02-17 Paper/MSRChallenge2017.tex
rewrote part of the evaluation section

To do this, we extracted from the original file provided~\cite{msr17challenge} 
the commit hash and the project name. We removed the repeated rows and created a 
script to gather the social data of the developer who pushed that commit.
First we concatenated the two attributes before mentioned in the following way:
\newline \newline
\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
\newline \newline
We created a script that constructs this string and navigates through the html 
representation of the website described above, and looks for the 
\textit{username} of the developer in the Github platform. If it is able to find 
one, we then create another string following the pattern:
\newline \newline
\textit{https://github.com/\textbf{UserName}}
\newline \newline
We then navigate through the html representation of the developer's profile 
website (described above) and gather the following attributes:
\begin{itemize}
\item Repositories
\item Stars
\item Followers
\item Following
\item ContribProjects
\end{itemize}

Repositories alludes to the repositories the developer has access to. This 
includes where the developer is the repository owner,where the developer is a 
collaborator, and repositories that the developer can access through an 
organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
show the projects the developer has stared, where starring translates to showing 
appreciation to the repository and creating a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
Following detail the number of developers that are following and being followed 
by the developer in question. Finally, the last attribute studies is the number 
of contributions made by the developer in the last year. To this dataset, we 
also added from the original dataset provided~\cite{msr17challenge} the 
attribute gh\_by\_core\_team\_member which we considered to have also social 
weight, which describes if the developer pushing the commit is a core member of 
the project the commit is being pushed to.

@@

\section{Evaluation}
\todo{I guess we have to remove the logisitic regression section here if we are not going to present those results. Depending on what Bogdan and Claire think.}
To evaluate the predictive power we can gain from analyzing the corpus 
provided~\cite{msr17challenge}, we have created a logistic regression model from 
both the datasets described in Section \ref{approach}. A logistic regression 
model is one where the dependent variable is categorial~\cite{freedman09}. Since 
in this study we are interested only in the cases where the commit was 
successfully integrated against any other possible state (errored, failed, 
canceled, started), we have divided our corpus into only two possible states, 
successful and notSuccessful, as to have a binary dependent variable.

A binary logistic model is a mechanism used to calculate the probability of 
characterizing a binary dependent variable based on one or more independent 
variables~\cite{walker67,cox58}. In our study, the binary dependent variable 
would become the final status of the Travis CI jobs triggered by the commit 
pushed by the developer, and the independent variables are both the technical 
attributes (files added, files deleted, source churn, etc) and the social 
attributes (stars, followers, repositories, etc.) used to predict the the class 
value.

We also evaluate our dataset by using decision trees, a predictive model which 
branches the different possible class values (represented as the leaves) 
depending on the attributes used to predict the class value (represented as the 
branches). In classification trees as the one being used in this study, each 
attribute represents a branch (with some exceptions due to pruning) and 
depending on the decisions taken while traversing the tree, the class value will 
be determined when one of the decisions leads to a leaf of the tree, therefore a 
class value will be encountered and a prediction can be made.

>>>>

To do this, we extracted from the original file provided~\cite{msr17challenge} 
the commit hash and the project name. We removed the repeated rows and created a 
script to gather the social data of the developer who pushed that commit.
First we concatenated the two attributes before mentioned in the following way:
\newline \newline
\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
\newline \newline
We created a script that constructs this string and navigates through the html 
representation of the website described above, and looks for the 
\textit{username} of the developer in the Github platform. If it is able to find 
one, we then create another string following the pattern:
\newline \newline
\textit{https://github.com/\textbf{UserName}}
\newline \newline
We then navigate through the html representation of the developer's profile 
website (described above) and gather the following attributes:
\begin{itemize}
\item Repositories
\item Stars
\item Followers
\item Following
\item Contributions 
\end{itemize}

Repositories alludes to the repositories the developer has access to. This 
includes where the developer is the repository owner,where the developer is a 
collaborator, and repositories that the developer can access through an 
organization membership.\footnote{https://developer.github.com/v3/repos/} Stars 
show the projects the developer has stared, where starring translates to showing 
appreciation to the repository and creating a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/} Followers and 
Following detail the number of developers that are following and being followed 
by the developer in question. Finally, the last attribute studied is the number 
of contributions made by the developer in the last year. To this dataset, we 
also added from the original dataset provided~\cite{msr17challenge} the 
attribute gh\_by\_core\_team\_member which we considered to have also social 
weight, which describes if the developer pushing the commit is a core member of 
the project the commit is being pushed to.

@@

\section{Evaluation}
\todo{I guess we have to remove the logisitic regression section here if we are not going to present those results. Depending on what Bogdan and Claire think.}
\todo{consider moving this data preprocessing step to the previous section}
To explore how much social aspects contributed to the build success, we first
converted the build statuses to successful (passed) and not successful (errored,
failed, canceled, and started).  We then created a decision tree classifier
using the technical data to establish how influential the technical data is on 
build success.  We then added the social data to the technical data and used
that to create a new decision tree classifier.  The decision trees were
evaluated using ten fold cross validation.

\todo{this paragraph is now out of place.  Decide where to move it.}
We also evaluate our dataset by using decision trees, a predictive model which 
branches the different possible class values (represented as the leaves) 
depending on the attributes used to predict the class value (represented as the 
branches). In classification trees as the one being used in this study, each 
attribute represents a branch (with some exceptions due to pruning) and 
depending on the decisions taken while traversing the tree, the class value will 
be determined when one of the decisions leads to a leaf of the tree, therefore a 
class value will be encountered and a prediction can be made.
